Optimal (Multiway) Spatial Joins

### 2024-05-29 4.2.tex
4.2

Finally, we prove (3). 
For each $\bm{t'}\in  \J(R_1',...,R_{k-2}')$ and each $h \in \dcross_H(\bm{t'})$, we will identify a unique tuple $\bm{t}$ in $\J(R_1,...,R_{k-2},H,V)$ defined as follows. Let $r_i$ be the full rectangle of $r_i'$ for $i \in [k]$, and $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. Let $\bm{t} = (r_1,...,r_{k-2},h,v)$. Since $h$ crosses $B_{\bm{t'}}$ by the definition of $\dcross_H(\bm{t'})$, the $h\cap v$ is a point in $B_{\bm{t'}}$. 
Therefore, $h\cap v \in B_{\bm{t'}} \subseteq B_{\bm{t}}$, and $\bm{t}\in \J(R_1,...,R_{k-2},H,V)$. As a result, $\sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}  |\dcross_H(\bm{t})| \leq \out$.

>>>>

Finally, we prove (3). 
For each $\bm{t'}\in  \J(R_1',...,R_{k-2}')$ and each $h \in \dcross_H(\bm{t'})$, we will identify a unique tuple $\bm{t}$ in $\J(R_1,...,R_{k-2},H,V)$ defined as follows. Let $r_i$ be the full rectangle of $r_i'$ for $i \in [k]$, and $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. Let $\bm{t} = (r_1,...,r_{k-2},h,v)$. Since $h$ crosses $B_{\bm{t'}}$ by the definition of $\dcross_H(\bm{t'})$, the $h\cap v$ is a point in $B_{\bm{t'}}$. 
Therefore, $h\cap v \in B_{\bm{t'}} \subseteq B_{\bm{t}}$, and $\bm{t}\in \J(R_1,...,R_{k-2},H,V)$. he result tuple is unique because for any two distinct tuples $\bm{t'_1}$ and $\bm{t'_2}$ in $\J(R_1',...,R_{k-2}')$, there exists an integer $i \in [k-2]$ s.t. the full rectangles of $\bm{t'_1}[i]$ and $\bm{t'_2}[i]$ are different, which means the $i$-th component of their associating tuples $\bm{t_1}, \bm{t_2} \in \J(R_1,...,R_{k-2},H,V)$ are different. As a result, $\sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}  |\dcross_H(\bm{t})| \leq \out$.
